---
title: "Final_Proj"
author: "Freddy Xu"
date: "4/18/2017"
output: html_document
---

## Packages

```{r chunk1, warning = FALSE, results = "hide"}
library(data.table)
library(dplyr)
library(glmnet)
```

## Downloading data

Renamed datasets to "business_test, "business_train", "checkin", "tip", "review_test", "review_train", and "user".

```{r chunk2, warning = FALSE}
setwd("~/Desktop/Final_Proj")
busi_trn = data.table(read.csv("business_train.csv"))
busi_tst = data.table(read.csv("business_test.csv"))
revw_trn = data.table(read.csv("review_train.csv"))
revw_tst = data.table(read.csv("review_test.csv"))
ckin = data.table(read.csv("checkin.csv"))
tips = data.table(read.csv("tip.csv"))
user = data.table(read.csv("user.csv"))
```

```{r chunk3, warning = FALSE}
busi_trn = busi_trn[,-c("X","type")]
busi_tst = busi_tst[,-c("X","Unnamed..0","type")]
revw_trn = revw_trn[,-c("X","type")]
revw_tst = revw_tst[,-c("X","type")]

ckin = ckin[,-c("X","type")]
tips = tips[,-c("X","type")]
user = user[,-c("X","type")]
```

## Star Rating Prediction

In reviews, stars are given on a scale of 1.0 to 5.0, on increments of 1.0, for a total of 5 possibilities.
In comparison, for businesses, stars are given on a scale of 1.0 to 5.0, on increments of 0.5, for a total of 9 possibilities.

```{r chunk4, warning = FALSE}
revw_num = revw_trn[,c("funny","useful","cool","stars")]
revw_cls = kmeans(revw_num[,c("funny","useful","cool")], 5)
# aggregate(revw_num[,c("funny","useful","cool","stars")], by = list(revw_cls$cluster), FUN = mean)

cluster = function(lst, cluster) {
  distance = function(vec1, vec2) {
    return(sqrt(sum((vec1 - vec2)^2)))
  }
  dists = rep(0,nrow(cluster$centers))
  for (i in 1:length(dists)) {
    cent = cluster$centers[i,1:length(lst)]
    dists[i] = distance(lst, cent)
  }
  return(which.min(dists))
}
```


## Attribute Parsing

```{r chunk5}
attr = function(lst, table, num) {
  need = function(char) {
    if (char %in% c(letters, LETTERS)) {
      return(TRUE)
    } else {
     return(!(is.na(as.numeric(char)))) 
    }
  }

  find = function(ind, dir) {
    ind1 = ind + dir
    while(!need(substr(text, ind1, ind1))) {
      if(substr(text, ind1, ind1) == "{") {
        return("")
      } else {
        ind1 = ind1 + dir
      }
    }

    ind2 = ind1 + dir
    while(need(substr(text, ind2, ind2))) {
      ind2 = ind2 + dir
    }
    ind2 = ind2 - dir

    return(substr(text, min(ind1, ind2), max(ind1, ind2)))
  }

  proper = function(str) {
    return(paste0(toupper(substr(str, 1, 1)), substring(str, 2)))
  }

  text = factor(lst)
  posi = 1
  while(substr(text, posi, posi) != "") {
    if (substr(text, posi, posi) == ":") {
      col = proper(find(posi, -1))
      val = tolower(find(posi, 1))
      if (val != "") {
        if (val %in% c("true", "yes", "formal", "full", "free", "very", "4")) {
          val = 1
        } else if (val %in% c("loud", "3")) {
          val = 0.66
        } else if (val %in% c("dressy", "beer", "paid")) {
          val = 0.5
        } else if (val %in% c("average", "2")) {
          val = 0.33
        } else if (val %in% c("false", "no", "casual", "none", "no", "quiet", "1"))  {
          val = 0
        }
        if (!(col %in% colnames(table))) {
          table[,col] = as.numeric(NA)
        }
        table[num,col] = val
      }
    }
    posi = posi + 1
  }
  return(table)
}
```

```{r chunk6, warning = FALSE}
busi_att = busi_trn
for(i in 1:nrow(busi_att)) {
  busi_att = attr(busi_att$attributes[i], busi_att, i)
}

rm(i)
```

```{r chunk7, warning = FALSE}
remove = c()
for(i in 1:ncol(busi_att)) {
  if(sum(table(busi_att[,i, with = FALSE])) <= 0.1 * nrow(busi_att)) {
    remove = append(remove, colnames(busi_att)[i])
  }
}
busi_cln = busi_att[,-remove, with = FALSE][,-"attributes"]

# remove = c()
# for(i in 1:nrow(busi_cln)) {
#   if(count number of nas from 15:ncol(busi_cln)) {
#     remove = append(remove, i)
#   }
# }
# busi_cln = busi_cln[-remove]

rm(i, remove)
```

```{r chunk8, warning = FALSE}
# pred = data.matrix(busi_cln[,(ncol(busi_trn)+1):ncol(busi_cln)])
# pred[is.na(pred)] = 0
# cvfit = cv.glmnet(x = pred, y = busi_cln$stars)
# coef(cvfit, s = "lambda.1se")
```

## Checkin Parsing

```{r chunk9}
aggr = function(lst, table, num) {
  text = lst$time

  get_wday = function(ind) {
    return(substr(text, ind - 3, ind - 1))
  }

  get_hour = function(ind) {
    ind2 = ind
    while(substr(text, ind2, ind2) != ":") {
      ind2 = ind2 + 1
    }
    return(substr(text, ind + 1, ind2 - 1))
  }

  get_chks = function(ind) {
    while(substr(text, ind, ind) != ":") {
      ind = ind + 1
    }
    ind2 = ind
    while(substr(text, ind2, ind2) != "'") {
      ind2 = ind2 + 1
    }
    return(as.numeric(substr(text, ind + 1, ind2 - 1)))
  }

  posi = 1
  while(substr(text, posi, posi) != "") {
    if(substr(text, posi, posi) == "-") {
      wday = get_wday(posi)
      hour = get_hour(posi)
      chks = get_chks(posi)
      table[num,wday] = table[num,wday, with = FALSE] + chks
      table[num,hour] = table[num,hour, with = FALSE] + chks
    }
    posi = posi + 1
  }
  return(table)
}
```

```{r chunk10, warning = FALSE}
ckin_cnt = ckin
ckin_cnt[,c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun")] = 0
ckin_cnt[,sprintf("%01.0f", 0:9)] = 0
ckin_cnt[,sprintf("%02.0f", 10:23)] = 0
ckin_cnt[,"Total"] = 0
for(i in 1:nrow(ckin_cnt)) {
  ckin_cnt = aggr(ckin_cnt[i,1], ckin_cnt, i)
  ckin_cnt[i,"Total"] = sum(ckin_cnt[i,3:9])
}

rm(i)
```

```{r chunk11, warning = FALSE}
inc_ckin = c()
for(i in 1:nrow(ckin_cnt)) {
  if (!(ckin_cnt$business_id[i] %in% busi_trn$business_id) &&
      !(ckin_cnt$business_id[i] %in% busi_tst$business_id)) {
    inc_ckin = c(inc_ckin, i)
  }
}
if (!(is.null(inc_ckin))) {
  ckin_cnt = ckin_cnt[-inc_ckin,]
}

rm(i, inc_ckin)
```

## Review

```{r chunk12}
diff_avg = function(plain, grouped, col, avg, dis) {
  for(i in 1:nrow(plain)) {
    plain[i,dis] = abs(grouped[,avg][(grouped$business_id == plain$business_id[i]) &
                                (grouped[[col]] == plain[i,col][[1]]),]
                      - plain$stars[i])
  }
  return(plain)
}
```

```{r chunk13, warning = FALSE}
revw_dis = revw_trn
revw_dis$date = as.character(revw_dis$date)
revw_dis$month = as.numeric(substr(revw_dis$date, 6, 7))
revw_dis = revw_dis %>% mutate(season = (((month - 1) %/% 3) + 1))
revw_dis[,c("seasonal_dist", "monthly_dist")] = 0

revw_mon = revw_dis[,c("business_id", "stars", "month")] %>%
  group_by(business_id, month) %>%
  summarise(monthly_avg = mean(stars))
revw_sea = revw_dis[,c("business_id", "stars", "season")] %>%
  group_by(business_id, season) %>%
  summarise(seasonal_avg = mean(stars))

revw_dis = diff_avg(revw_dis, revw_mon, "month", "monthly_avg", "monthly_dist")
revw_dis = diff_avg(revw_dis, revw_sea, "season", "seasonal_avg", "seasonal_dist")

rm(revw_mon, revw_sea)
```

x = "yy:mm:dd:hh:mm:ss:mi"
y = yymmdd

day = substr(x,7,8)

lubridate:ms(x, day)